Tables and Figures

### 2024-01-04 analysis/paper/fig_tab.Rmd
update dependencies

```{r setup-figs-and-tbls, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
```

>>>>

```{r setup-figs-and-tbls, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
```
